\begin{thebibliography}{99}

    \bibitem{shopifyblog} 
    Shopify. \textit{What is Shopify?}. Available at: \url{https://www.shopify.com/blog/what-is-shopify}

    \bibitem{sdlc} 
    LTS Group. \textit{SDLC - Software Development Life Cycle}. Available at: \url{https://ltsgroup.tech/blog/sdlc-software-development-life-cycle/}

    \bibitem{scrumframework} 
    Aymen Chaqrouf. \textit{Comment l'utilisation d'une méthodologie de gestion des projets Agile peut améliorer la performance de votre équipe}. Available at: \url{https://www.linkedin.com/pulse/comment-lutilisation-dune-m%C3%A9thodologie-de-gestion-des-aymen-chaqrouf/}

    \bibitem{ganttchart} 
    Online Gantt. \textit{Online Gantt Chart Tool}. Available at: \url{https://www.onlinegantt.com/#/gantt}

    \bibitem{nodejs} 
    Node.js. \textit{Node.js® is a free, open-source, cross-platform JavaScript runtime environment that lets developers create servers, web apps, command line tools and scripts}. Available at: \url{https://nodejs.org/en}
        
    \bibitem{expressjs} 
    Express.js. \textit{Express is a minimal and flexible Node.js web application framework that provides a robust set of features for web and mobile applications}. Available at: \url{https://expressjs.com}
        
    \bibitem{golang} 
    FreeCodeCamp. \textit{What is Go Programming Language?}. Available at: \url{https://www.freecodecamp.org/news/what-is-go-programming-language/#heading-whats-the-name-go-or-golang}
        
    \bibitem{rabbitmq} 
    CloudAMQP. \textit{RabbitMQ for Beginners - What is RabbitMQ?}. Available at: \url{https://www.cloudamqp.com/blog/part1-rabbitmq-for-beginners-what-is-rabbitmq.html#:~:text=RabbitMQ%20is%20a%20message-queueing,include%20any%20kind%20of%20information.}
        
    \bibitem{vite} 
    Dev.to. \textit{Best Practices for Using TypeScript in React with Vite}. Available at: \url{https://dev.to/oppaaaii/best-practices-for-using-typescript-in-react-with-vite-1dhf}
        
    \bibitem{reactnative} 
    Wikipedia. \textit{React Native}. Available at: \url{https://en.wikipedia.org/wiki/React_Native}
        
    \bibitem{expo} 
    Expo. \textit{Expo GitHub Repository}. Available at: \url{https://github.com/expo/expo/blob/main/README.md}
        
    \bibitem{zustand} 
    Zustand. \textit{Getting Started - Introduction}. Available at: \url{https://zustand.docs.pmnd.rs/getting-started/introduction}
        
    \bibitem{mongodb} 
    MongoDB. \textit{What is MongoDB?}. Available at: \url{https://www.mongodb.com/company/what-is-mongodb}
        
    \bibitem{mongoose} 
    FreeCodeCamp. \textit{Introduction to Mongoose for MongoDB}. Available at: \url{https://www.freecodecamp.org/news/introduction-to-mongoose-for-mongodb-d2a7aa593c57/}
        
    \bibitem{redis} 
    Redis. \textit{About Redis}. Available at: \url{https://redis.io/about/}

    \bibitem{convertywebsite} 
    Converty. \textit{About Converty}. Available at: \url{https://www.converty.com/about}

\end{thebibliography}