\chapter*{General Introduction}
\markboth{General Introduction}{General Introduction}

Over the past decade, the e-commerce industry in the MENA region has experienced significant growth. However, the development and adoption of online payment services have not kept pace with this expansion, leading to a substantial gap between demand and availability. As a result, cash-on-delivery (COD) has become the predominant payment method, fueling the sector's growth.

E-commerce platforms like Shopify are well known for their dominance in online retail, especially in the drop shipping sector. Despite its flexibility, Shopify’s extensive feature set can cause performance issues and a steep learning curve for new users. The high number of applications required for various functionalities, each with its own subscription fee, presents a barrier to small businesses. Moreover, the platform’s level of abstraction makes extensive customization challenging.

To address these challenges, Converty was created with a focus on enhancing user efficiency and customization. Converty offers a comprehensive CRM and CMS platform designed to streamline the creation of high-converting online stores and manage all aspects of a business from a single platform. This approach eliminates the need for coding, spreadsheets, and additional applications, simplifying the management process.

During my six-month internship at Converty, I worked on resolving critical issues within the CRM and CMS dashboards, addressing performance-related concerns, and completing the mobile app experience. My tasks included enhancing existing features, implementing new functionalities, and improving the overall user experience on the dashboard and the mobile app.

This report provides an in-depth analysis of my internship experience, detailing the challenges encountered, the solutions implemented, and the lessons learned. It is structured as follows:

The first chapter, "Project Overview," covers the scope of the internship, the specific problems addressed, and the objectives of the internship with actionable items. It includes sections on the host company, Converty, its services, a study of the existing solutions, the problem statement, the proposed solution, and details about the project such as goals, objectives, deliverables, management plan, timeline, and a conclusion.

The second chapter, "Analysis and Specification of Requirements," includes an introduction, functional and non-functional requirements, analysis of requirements, identification of system actors, a global use case diagram, and a refinement of use cases.

The third chapter, "Project Architecture \& Choice Of Technologies," describes the architecture that the project will follow and the technologies that will be used.

The fourth chapter, "Realization - Web Features," details the web features developed during the internship.

The fifth chapter, "Realization - Mobile Features," details the mobile features developed during the internship.

The report concludes with a general conclusion and the perspectives of the project.