\chapter{Perspectives and Conclusion}

In this internship, we had the opportunity to work on a real-world project, which provided us with invaluable experience in the software development process and team collaboration. We learned how to effectively use various technologies and tools to build a scalable and performant system. Despite facing numerous challenges throughout the internship, we overcame them through teamwork and continuous learning. We are proud of our accomplishments and are excited to see the project go live.

Our journey began with a deep dive into understanding the project requirements and familiarizing ourselves with the technologies we would be using. We then moved on to designing the system architecture and implementing the core features.

We started by laying the foundation in \textbf{Sprint 1}, where we recreated a simple template to establish a solid starting point for the project.

In \textbf{Sprint 2}, we enhanced the system's marketing capabilities by implementing upsell and cross-sell functionalities, providing additional value to the platform’s users.

\textbf{Sprint 3} focused on the mobile aspect, where we developed comprehensive order management features. These features included displaying, adding, editing, filtering, and searching orders, ensuring that users could efficiently manage their orders within the mobile app.

Moving forward, \textbf{Sprint 4} was dedicated to implementing budget and cost management features in the mobile app, allowing users to effectively manage their finances within the platform.

In \textbf{Sprint 5}, we introduced a statistics management feature, enabling users to view and filter various types of statistical data. This added analytical capabilities to the platform, helping users make informed decisions.

Finally, in \textbf{Sprint 6}, we significantly improved user engagement by implementing real-time notifications using Socket.IO. This feature ensured that users were always updated with the latest information, enhancing the overall user experience.

Throughout these sprints, we adhered to a modular monolith architecture, ensuring that each component of the system was well-defined and maintainable. We utilized a variety of technologies, including Node.js with Express for the backend, React for the web dashboard, React Native for the mobile app, and MongoDB for the database.

This internship has been a rewarding experience, allowing us to apply our skills in a practical setting and gain new insights into software development. We look forward to the project's future success and its positive impact on users.

\section*{Future Work}
Looking ahead, there are several areas where the project can be expanded and improved:

\subsection*{Advanced Features}
We plan to implement additional features such as advanced analytics, AI-driven recommendations, and enhanced SEO tools. These features will provide users with deeper insights, personalized experiences, and better visibility in search engines.

\subsection*{Localization Expansion}
To cater to a global audience, we aim to add support for more languages and adapt the platform for different regional markets. This will involve translating the user interface, adjusting content to fit cultural contexts, and ensuring compliance with local regulations.